A Logical Solution of the Linearity Challenge

### 2025-08-01 paper/calculus.tex
drafted type safety

As usual, we write $\ReductionContext[P]$ for the process obtained by replacing
the hole in $\ReductionContext$ with $P$, noting that such replacement may
capture channel names that are bound in $\ReductionContext$ and occur free in
$P$.
%
Now we observe that if $P$ and $Q$ both act on the same channel $x$ in
complementary ways, then their parallel composition $\Cut\x{P}{Q}$ is reducible
according to one of the principal cut reductions described in
\Cref{tab:semantics}. Therefore, an alternative (and more general) way of
formulating well formedness is this:
%
we say that $P$ is \emph{well formed} if $P \pcong
\ReductionContext[\Cut\x{Q_1}{Q_2}]$ implies that $\Cut\x{Q_1}{Q_2}$ is alive.

>>>>

As usual, we write $\ReductionContext[P]$ for the process obtained by replacing
the hole in $\ReductionContext$ with $P$, noting that such replacement may
capture channel names that are bound in $\ReductionContext$ and occur free in
$P$.
%
Now we observe that if $P$ and $Q$ both act on the same channel $x$ in
complementary ways, then their parallel composition $\Cut\x{P}{Q}$ is reducible
according to one of the principal cut reductions described in
\Cref{tab:semantics}. Therefore, an alternative (and more general) way of
formulating well formedness is simply this:
%
we say that $P$ is \emph{well formed} if $P \pcong \ReductionContext[Q]$ implies
that $Q$ is alive.
